### 2020-02-14 README.Rmd
Reorganizing README

| input\_model | input\_corpus | output                                                                          |
|--------------|:-------------:|---------------------------------------------------------------------------------|
| Not NULL     | NULL          | oolong test for a topic model with word intrusion test                          |
| Not NULL     | Not NULL      | oolong test for a topic model with word intrusion test and topic intrusion test |
| NULL         | Not NULL      | oolong test for creating gold standard                                          |
| NULL         | NULL          | error                                                                           |

>>>>

| input\_model | input\_corpus | output                                                                                                                           |
|--------------|:-------------:|----------------------------------------------------------------------------------------------------------------------------------|
| Not NULL     | NULL          | oolong test for a topic model with [word intrusion test](#word-intrusion-test)                                                   |
| Not NULL     | Not NULL      | oolong test for a topic model with [word intrusion test](#word-intrusion-test) and [topic intrusion test](#topic-intrusion-test) |
| NULL         | Not NULL      | oolong test for [creating gold standard](#creating-gold-standard)                                                                |
| NULL         | NULL          | error                                                                                                                            |
